|

### 2023-04-11 paper/04-results.Rmd
Begin initial description of multilevel model results

@@

icc
rusher 0.0574
blocker 0.0121
passer 0.0233
Residual 0.907

>>>>

There are a variety of quantities we're interested in from the multilevel model fit in Section [INSERT SECTION REF]. First, Table [FIXED EFFECTS REF] displays the results for the fixed effects terms. [INSERT CONCLUSIONS ABOUT THESE VARIABLES]  Next, Table [INSERT ICC TABLE REF] displays the intraclass correlation coefficients (ICC) for the three different grouped terms, describing the proportion variance explained between the group terms in comparison to the residual variance. While the residual variance is unsurprisingly the largest value, between the three group terms, we observe the largest ICC for pass rushers, followed by the QB, and the blocker. This emphasizes how STRAIN is mostly attributable to pass rushers, but is necessary to adjust for opposition and other factors.

We display the random intercepts for pass rusher in Table [INSERT TABLE REFERENCE] alongside their unadjusted STRAIN values. We observe similar rankings based on the random intercepts in comparison to the average STRAIN, with Myles Garrett (DE), Aaron Donald (DT), Vita Vea (NT), and T.J. Watt (OLB) as the top pass rushers. In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN. Figure \ref{fig:fig_rankings_boot} displays the mean varying intercept for the top ten pass rushers for each position along with 95% confidence intervals generated by sampling from the posterior distributions via parametric bootstrapping using the `merTools` package [@knowlesmerTools, @gelman2006data]. We observe different levels of variability across these top players, with the only a subset of players with intervals strictly above zero.  [NEED TO THINK ABOUT WHAT MORE TO SAY HERE]

@@

MAKE THIS A TABLE
icc
rusher 0.0574
blocker 0.0121
passer 0.0233
Residual 0.907
